---
title: <span style="color:midnightblue">**Network analysis**</span>
author: "Bareket Karif"
date: "26 באפריל 2016"
output: html_document
---  

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 200)
```

## <span style="color:slateblue">**Grey's anatomy**</span>  
#### *[Data source](http://www.babelgraph.org/data/ga_edgelist.csv)*  
### <span style="color:lightslategrey">**Question 1 - a**</span>  

```{r include= TRUE, echo=FALSE, warning=FALSE}
library("downloader")
library(igraph)

file<-".\\ga_edgelist.csv"
if(!file.exists(file)){
  fileURL <- "http://www.babelgraph.org/data/ga_edgelist.csv"
  download.file(fileURL, destfile = file)
  # Always record the date
  dateDownloaded <- date()
  dateDownloaded
}

ga.data <- read.csv(file, header=TRUE)
g <- graph.data.frame(ga.data, directed=FALSE)
```

### <span style="color:lightslategrey">**edgelist data**</span>  
```{r include= TRUE, echo=FALSE, warning=FALSE}
V(g)$name  
```
___

##### <span style="color:lightslategrey">**Betweenness**</span>  
```{r include= TRUE, echo=FALSE, warning=FALSE}
betweenness<-betweenness(g)
maximum_betweenness<-which.max(betweenness)
V(g)$name[maximum_betweenness]
```


we got that **the betweenness is sloan**.  
    
___  
  
	
##### <span style="color:lightslategrey">**Closeness**</span>  
```{r include= TRUE, echo=FALSE, warning=FALSE}
closeness<-closeness(g)
maximum_closeness<-which.max(closeness)
V(g)$name[maximum_closeness]
```

we got that **the closeness is torres**.  
  
___  
  
	
##### <span style="color:lightslategrey">**Eigencetor**</span>  
```{r include= TRUE, echo=FALSE, warning=FALSE}
eigencetor<-eigen_centrality(g)
maximum_eigencetor<-which.max(eigencetor$vector)
V(g)$name[maximum_eigencetor]
```

we got that **the eigencetor is karev**.   
  
___  
  
  
  
            

### <span style="color:lightslategrey">**Question 1 - b**</span>  
##### <span style="color:lightslategrey">**first algorithm**</span>  
```{r include= TRUE, echo=FALSE, warning=FALSE}
communitys<-g
```

**i. Print the networks by color code corresponding to the communities**
```{r include= TRUE, echo=FALSE, warning=FALSE}
fc <- walktrap.community(communitys)
plot(fc,communitys,vertex.label=membership(fc))
```


**ii. How communities received by each algorithm. What their size?**
```{r include= TRUE, echo=FALSE, warning=FALSE}
sizes(fc)
```  

  

**iii. What is the value of modularity received?**
```{r include= TRUE, echo=FALSE, warning=FALSE}
modularity(fc)
```  
___
##### <span style="color:lightslategrey">**second algorithm**</span>  
**i. Print the networks by color code corresponding to the communities**
```{r include= TRUE, echo=FALSE, warning=FALSE}
fc <- edge.betweenness.community(communitys)
plot(fc,communitys,vertex.label=membership(fc))
```


**ii. How communities received by each algorithm. What their size?**
```{r include= TRUE, echo=FALSE, warning=FALSE}
sizes(fc)
```  

  

**iii. What is the value of modularity received?**
```{r include= TRUE, echo=FALSE, warning=FALSE}
modularity(fc)
``` 
  
  
  
  
  
## <span style="color:slateblue">**Analyze dolphins data**</span>  
#### *[Data source](http://www-personal.umich.edu/~mejn/netdata/dolphins.zip)*  

### <span style="color:lightslategrey">**Question 2 - a**</span>  
  
```{r include= TRUE, echo=FALSE, warning=FALSE}
library(igraph)
g <- read.graph("dolphins.gml", format = c("gml"))
```

### <span style="color:lightslategrey">**Date Description:**</span>  
The file dolphins.gml contains an undirected social network of frequent
associations between 62 dolphins in a community living off Doubtful Sound,
New Zealand, as compiled by Lusseau et al. (2003).  Please cite

  D. Lusseau, K. Schneider, O. J. Boisseau, P. Haase, E. Slooten, and
  S. M. Dawson, The bottlenose dolphin community of Doubtful Sound features
  a large proportion of long-lasting associations, Behavioral Ecology and
  Sociobiology 54, 396-405 (2003).

Additional information on the network can be found in

  D. Lusseau, The emergent properties of a dolphin social network,
  Proc. R. Soc. London B (suppl.) 270, S186-S188 (2003).

  D. Lusseau, Evidence for social role in a dolphin social network,
  Preprint q-bio/0607048 (http://arxiv.org/abs/q-bio.PE/0607048)

### <span style="color:lightslategrey">**edgelist data**</span>  
```{r include= TRUE, echo=FALSE, warning=FALSE}
V(g)$label  
```
___

##### <span style="color:lightslategrey">**Betweenness**</span>  
```{r include= TRUE, echo=FALSE, warning=FALSE}
betweenness<-betweenness(g)
maximum_betweenness<-which.max(betweenness)
V(g)$label[maximum_betweenness]
```


we got that **the betweenness is SN100**.  
    
___  
  
	
##### <span style="color:lightslategrey">**Closeness**</span>  
```{r include= TRUE, echo=FALSE, warning=FALSE}
closeness<-closeness(g)
maximum_closeness<-which.max(closeness)
V(g)$label[maximum_closeness]
```

we got that **the closeness is SN100**.  
  
___  
  
	
##### <span style="color:lightslategrey">**Eigencetor**</span>  
```{r include= TRUE, echo=FALSE, warning=FALSE}
eigencetor<-eigen_centrality(g)
maximum_eigencetor<-which.max(eigencetor$vector)
V(g)$label[maximum_eigencetor]
```

we got that **the eigencetor is Grin**.   
  
___  
  
  
  
            

### <span style="color:lightslategrey">**Question 2 - b**</span>  
##### <span style="color:lightslategrey">**first algorithm**</span>    
```{r include= TRUE, echo=FALSE, warning=FALSE}
communitys<-g
```

**i. Print the networks by color code corresponding to the communities**
```{r include= TRUE, echo=FALSE, warning=FALSE}
fc <- walktrap.community(communitys)
plot(fc,communitys,vertex.label=membership(fc))
```


**ii. How communities received by each algorithm. What their size?**
```{r include= TRUE, echo=FALSE, warning=FALSE}
sizes(fc)
```  

  

**iii. What is the value of modularity received?**
```{r include= TRUE, echo=FALSE, warning=FALSE}
modularity(fc)
```  
___
##### <span style="color:lightslategrey">**second algorithm**</span>  
**i. Print the networks by color code corresponding to the communities**
```{r include= TRUE, echo=FALSE, warning=FALSE}
fc <- edge.betweenness.community(communitys)
plot(fc,communitys,vertex.label=membership(fc))
```


**ii. How communities received by each algorithm. What their size?**
```{r include= TRUE, echo=FALSE, warning=FALSE}
sizes(fc)
```  

  

**iii. What is the value of modularity received?**
```{r include= TRUE, echo=FALSE, warning=FALSE}
modularity(fc)
``` 
